---
title: "Lab 1 Report"
author: "Tyler Wiederich"
date: "2/11/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 6, fig.height = 2.5)
library(tidyverse)
library(ggpubr)
library(broom)

orig <- readxl::read_excel('Lab 1 Data.xlsx')

df <- janitor::clean_names(orig)# %>% filter(participant < 5)
df$participant <- as.character(df$participant)
```



# Introduction

In this lab, we are exploring response times the Shapesplosion game at https://stat2games.sites.grinnell.edu. Our study consists of four subjects, each of whom has played each matching scheme one time and recorded their times. 

# Methods

# Results

For our analysis, we conducted a one-way blocked analysis of variance. Taking a look at Figure 1, we can 

```{r, echo=FALSE, fig.cap='Boxplot of Response Times by Game'}
ggpubr::ggboxplot(df, 'shapesplosion', 'time_seconds') +
  labs(x = 'Game', y = 'Time (in seconds)') +
  ggtitle('Time Response for Shapesplosion Games')

```

In Table 1, we can see, at the $\alpha=0.05$ level that there is evidence to suggest that the response times are different across the Shapesplosion Games.

```{r, fig.cap='Table 1', echo=FALSE}
mod <- lm(time_seconds ~ shapesplosion + participant, 
          data = df)
knitr::kable(tidy(round(anova(mod),4)))
```


# Discussion and Conclusion



